Top-down and bottom-up cohesiveness\\in microbial community coalescence

### 2021-05-27 draft/draft_v3.tex
typos

Our minimal model is set within the same MicroCRM framework that we used
for the previous simulations.
As described in the main text, the model contains two communities
of two species each
($\mathrm{s}_1$ to $\mathrm{s}_4$),
with five resources in total, out of which the first one ($\mathrm{R}_1$)
is replenished externally at the beginning of each growth cycle
and the rest correspond to the species' metabolic byproducts.
Each species secretes a unique byproduct, meaning that the metabolic
matrix $\mathbf{D}$ is binary in this case.
The specific structure of $\mathbf{D}$ is displayed below
--because it is a 3-dimensional matrix in our framework,
we have ``sliced'' it into the five 2-dimensional matrices corresponding to
our five species.

>>>>

Our minimal model is set within the same MicroCRM framework that we used
for the previous simulations.
As described in the main text, the model contains two communities
of two species each
($\mathrm{s}_1$ to $\mathrm{s}_4$),
with five resources in total, out of which the first one ($\mathrm{R}_1$)
is replenished externally at the beginning of each growth cycle
and the rest correspond to the species' metabolic byproducts.
Each species secretes a unique byproduct, meaning that the metabolic
matrix $\mathbf{D}$ is binary in this case.
The specific structure of $\mathbf{D}$ is displayed below
--because it is a 3-dimensional matrix in our framework,
we have ``sliced'' it into the four 2-dimensional matrices corresponding to
our four species.
